Build Operating Models for SA Species

### 2022-03-29 BuildOM/BuildOMAssess2OM.Rmd
newest runs

run_rdat_to_Obs <- TRUE   # If TRUE, OM will start with ObsUser but then run rdat_to_Obs on the appropriate
                          # rdat to modify the Obs object to reflect sampling observed in data used in BAM
                          # assessments

@@

@@

```{r}
# create completely empty Data object
Data_empty <- local({
  dat <- new("Data")
  for(slotName_i in slotNames(dat)){
    slot_i <- slot(dat,slotName_i)
    if(length(slot_i)>0&is.numeric(slot_i)){
      slot(dat,slotName_i) <- slot_i*NA
    }
  }
  dat
})
```

@@

  Data_name_i <- gsub("rdat","Data",rdat_name_i)
  Data_i <- rdat_to_Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc,nsim=nsim)
  # This is to try to solve a problem that occurs later when running Simulate on OM_GreaterAmberjack that has something to do with CAL
  # I think it might be occurring because there are length comps in a year with no age comps. Maybe. It doesn't occur with Cobia which also
  # has CAL with values for only a single year.
  # if(Data_name_i=="Data_GreaterAmberjack"){
  #   Data_i@CAL <- array(NA,c(1,1,1))
  #   Data_i@CAL_bins <- as.numeric(NA)
  #   Data_i@CAL_mids <- as.numeric(NA)
  # }
  #Data_i@wla <- Data_i@wla*0.00220462 # Convert kg to klb

@@

```{r build OM Assess2OM, eval=TRUE}
list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc (for plotting hist compared to BAM)
vec_to_mat <- function(vec){
  matrix(vec,nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                    dimnames=dimnames(naa)[2:3])
}

mat_to_array <- function(mat,nsim){
  mat_data <- rep(as.numeric(mat),each=nsim)
  array(mat_data, dim=c(nsim,nrow(mat),ncol(mat)),
               dimnames=list("sim"=1:nsim, "ages"=rownames(mat), "year"=colnames(mat)))
}

for(rdat_name_i in bam_rdat_sub){
  rdat_i <- standardize_rdat(get(rdat_name_i))
  Name_i <- gsub("rdat_","",rdat_name_i)
  DataName_i <- gsub("rdat_","Data_",rdat_name_i)
  Data_i <- get(DataName_i)
  Obs_i <- rdat_to_Obs(rdat_i)

@@

  naa_mat <- cbind("age"=ageinit_i,t(rdat_i$N.age[years_i,]))
  naa_mat2 <- data_polate(naa_mat,xout = age_i)
  rownames(naa_mat2) <- age_i
  naa_mat2["0",-1] <- naa_mat2[paste(ageinitmin_i),-1]*Nage_F0_pr_sc # Compute numbers at age-0
  naa_mat2[naa_mat2<0] <- 1 # Don't let value be less than 1
  naa <- mat_to_array(naa_mat2[,-1],nsim=nsim)

@@

  faa <- mat_to_array(faa_mat2[,-1],nsim=nsim)

  mat_waa_klb <- matrix(a.series_i$wgt.klb,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  waa <- mat_to_array(mat_waa_klb,nsim=nsim)

  mat_pmat <- matrix(pmatage(a.series_i,herm=herm_i)$pmat,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  Mataa <- mat_to_array(mat_pmat,nsim=nsim)

  mat_M <- matrix(a.series_i$M,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  Maa <- mat_to_array(mat_M,nsim=nsim)

  mat_laa <- matrix(a.series_i$length*length_sc,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  laa <- mat_to_array(mat_laa,nsim=nsim)

@@

          if(!is.null(ObsUser)) {
          if(run_rdat_to_Obs){
            my_rdat <- get(gsub("OM","rdat",OM_name_i))
            ObsUser <- rdat_to_Obs(
                            rdat=my_rdat,
                            Obs=ObsUser,
                            Ind_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT"),
                            CAA_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT"),
                            CAL_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT")
                            )
          }
        }

 OM_i <- Assess2OM(Name=Name_i,
                proyears = proyears,
                interval = interval,
                CurrentYr = CurrentYr_i,
                h=steep_i, R0=R0_i,
                Obs = ObsUser,
                Imp = ImpUser,
                naa=naa, faa=faa, waa=waa, Mataa=Mataa, Maa=Maa, laa=laa,
                nyr_par_mu = 3,
                LowerTri = nyrNoRecDevEnd,
                recind = 0,
                plusgroup = TRUE,
                altinit = 0,
                fixq1 = TRUE,)

@@

 Data2_i <- Data_empty
 slot(Data2_i,"AddInd") <- AddInd
 slot(Data2_i,"CV_AddInd") <- CV_AddInd
 slot(Data2_i,"AddIndV") <- AddIndV
 slot(Data2_i,"AddIndType") <- AddIndType
 slot(Data2_i,"AddIunits") <- AddIunits

>>>>

run_rdat2Obs <- TRUE   # If TRUE, OM will start with ObsUser but then run rdat2Obs on the appropriate
                          # rdat to modify the Obs object to reflect sampling observed in data used in BAM
                          # assessments

@@

## Do not use age-varying M (since SCA uses constant M)
#!! As of 2022-03-24 the run_script for the MSE is expecting OM with age-varying M.
#!! M is then set to constant in most scenarios in the MSE
Mconstant <- FALSE

@@

@@

  Data_name_i <- gsub("rdat","Data",rdat_name_i)
  Data_i <- rdat2Data(rdat_i, Mat_age1_max=Mat_age1_max, length_sc = length_sc,nsim=nsim)

@@

```{r build OM Assess2OM, eval=TRUE}
list_Nage_F0_pr_sc <- list() # List for storing values of Nage_F0_pr_sc (for plotting hist compared to BAM)
vec2mat <- function(vec){
  matrix(vec,nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                    dimnames=dimnames(naa)[2:3])
}

mat2array <- function(mat,nsim){
  mat_data <- rep(as.numeric(mat),each=nsim)
  array(mat_data, dim=c(nsim,nrow(mat),ncol(mat)),
               dimnames=list("sim"=1:nsim, "ages"=rownames(mat), "year"=colnames(mat)))
}

for(rdat_name_i in bam_rdat_sub){
  rdat_i <- standardize_rdat(get(rdat_name_i))
  Name_i <- gsub("rdat_","",rdat_name_i)
  DataName_i <- gsub("rdat_","Data_",rdat_name_i)
  Data_i <- get(DataName_i)
  Obs_i <- rdat2Obs(rdat_i)

@@

  naa_mat <- cbind("age"=ageinit_i,t(rdat_i$N.age[years_i,]))
  naa_mat2 <- data_polate(naa_mat,xout = age_i)
  rownames(naa_mat2) <- age_i
  naa_mat2["0",-1] <- naa_mat2[paste(ageinitmin_i),-1]*Nage_F0_pr_sc # Compute numbers at age-0
  naa_mat2[naa_mat2<0] <- 1 # Don't let value be less than 1
  naa <- mat2array(naa_mat2[,-1],nsim=nsim)

@@

  faa <- mat2array(faa_mat2[,-1],nsim=nsim)

  mat_waa_klb <- matrix(a.series_i$wgt.klb,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  waa <- mat2array(mat_waa_klb,nsim=nsim)

  mat_pmat <- matrix(pmatage(a.series_i,herm=herm_i)$pmat,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  Mataa <- mat2array(mat_pmat,nsim=nsim)

  mat_M <- matrix(a.series_i$M,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  Maa <- mat2array(mat_M,nsim=nsim)

  mat_laa <- matrix(a.series_i$length*length_sc,
                        nrow=dim(naa)[2],ncol=dim(naa)[3],byrow=FALSE,
                        dimnames=dimnames(naa)[2:3])
  laa <- mat2array(mat_laa,nsim=nsim)

@@

          if(!is.null(ObsUser)) {
          if(run_rdat2Obs){
            my_rdat <- get(gsub("OM","rdat",OM_name_i))
            ObsUser <- rdat2Obs(
                            rdat=my_rdat,
                            Obs=ObsUser,
                            Ind_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT"),
                            CAA_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT"),
                            CAL_abb=c("sTV", "sCT", "sVD", "sBL", "sVL", "sBT", "sFT")
                            )
          }
        }

 OM_i <- Assess2OM(Name=Name_i,
                proyears = proyears,
                interval = interval,
                CurrentYr = CurrentYr_i,
                h=steep_i,
                R0=R0_i,
                Obs = ObsUser,
                Imp = ImpUser,
                naa=naa, faa=faa, waa=waa, Mataa=Mataa, Maa=Maa, laa=laa,
                nyr_par_mu = 3,
                LowerTri = nyrNoRecDevEnd,
                recind = 0,
                plusgroup = TRUE,
                altinit = 0,
                fixq1 = FALSE)

 if(Mconstant){
    OM_i@cpars$M_ageArray[] <- Data_i@Mort
 }

@@

 Data2_i <- Data_empty()
 slot(Data2_i,"AddInd") <- AddInd
 slot(Data2_i,"CV_AddInd") <- CV_AddInd
 slot(Data2_i,"AddIndV") <- AddIndV
 slot(Data2_i,"AddIndType") <- AddIndType
 slot(Data2_i,"AddIunits") <- AddIunits
